Phenomenological Robotics

### 2011-12-09 draft.tex
Added list of perceptual learning cases from E. Gibson.

>>>>

% Not present in the outline: learning process in infancy. This might not be the
% best place for this part, but it definitely goes together with the
% cornerstones of the framework below.
% (Source: Thesis journal, pages 140 to 149, 28/03/2011).
% (Source: \cite{gibson2000}, pages 134 to 149, chapter 8).

Gibson~\cite{gibson2000} affirms that perceptual learning predates birth. She
describes a number of cases, going from early perceptual learning to elaborate
sequences of action in older infants. In these cases, the infant learns:

\begin{itemize}
\item about oneself;
\item to control an event;
\item to perceive an unitary object;
\item what happens next in an observed event;
\item to participate in a communicative event;
\item to differentiate multimodally specified events;
\item distinctive features of things;
\item to use an object or an act as means;
\item about causal relations in observed events.
\end{itemize}
